Stabilization-Free Virtual Element Methods

### 2022-06-13 stabfreevem.tex
update

\begin{document}
\title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
\author{Chunyu Chen}%
\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
 \email{...@xtu.edu.cn}%
 \author{Xuehai Huang}%
 \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
 \email{huang.xuehai@sufe.edu.cn}%
\author{Huayi Wei}%
\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
 \email{weihuayi@xtu.edu.cn}%

@@

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
as shown in Figure \ref{fig:mesh}. The numerical results for $k = 1, 2, 5$ are 
listed in Figure \ref{fig:ncvemrate} \ref{fig:cvemrate}, 
where the errors use $L^2$ norm and $H^1$-like norm. Both cases confirm the
theoretic convergence rates.

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvemrate_convex.png}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvemrate_noconvex.png}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:ncvemrate}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvemrate_convex.png}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvemrate_noconvex.png}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:cvemrate}
\end{figure}

>>>>

\begin{document}
\title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
\author{Chunyu Chen}%
\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
 \email{202131510114@smail.xtu.edu.cn}%
 \author{Xuehai Huang}%
 \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
 \email{huang.xuehai@sufe.edu.cn}%
\author{Huayi Wei}%
\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
 \email{weihuayi@xtu.edu.cn}%

@@

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
as shown in Figure \ref{fig:mesh}. We use \eqref{eq:vem} and \eqref{eq:cfmvem} 
respectively to compute Example \ref{ex}, the numerical results for $k = 1, 2, 5$ are 
listed in Figure \ref{fig:rate1} \ref{fig:rate2}, 
where the errors use $L^2$ norm and $H^1$-like norm. Both cases confirm the
theoretical convergence rates.

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla_h u_h\|_0$ 
of $H^1$-nonconforming virtual element method on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{div}\nabla u_h\|_0$ 
of $H^1$-conforming virtual element method  on $\mathcal T_0$(left) and 
$\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate2}
\end{figure}
